---
title: "Shiny App. Probability of Surviving on Titanic"
author: "Dinara Satayeva"
date: "4/3/2020"
output:
  slidy_presentation: default
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Overview

The Shiny App: Probability of Surviving on Titanic is an interactive app that allows user to input some numbers and based on the numbers calculates probability of survival on Titanic. 

Moreover, the app shows a little os stats about people that were on Titanic, represented in graphs.

"Titanic.csv" dataset was used for calculations. 

First we built a logistic model, with categories shown on next slide as predictors. 

Then we used the newly produced model to predict aginst new dataset, built based on user input.

## Input numbers

- Age
- Sex
- Class
- Fare
- Number of children/parents aboard
- Number of siblings/spouses aboard

## Overview of the dataset

```{r echo = TRUE, comment = ""}
data<-read.csv("titanic.csv")
dim(data)
head(data)
```

## Summary of the logistic model

```{r }
fit<-glm(survived ~ pclass + sex + age + sib_sp + par_ch + fare, data = data, family = "binomial")
summary(fit)
```

## Ploting data
```{r}
pairs(~pclass+sex+age+sib_sp+par_ch+fare, data=data, cex.axis=1.5)
```